---
title: "COVID-19 Contact Tracing Report"
always_allow_html: true
output:
  rmarkdown::html_document:
    theme: cerulean
    toc: yes
    toc_depth: 2
    toc_float: yes
  rmarkdown::slidy_presentation:
    slide_level: 3
  pagedreport::paged_windmill:
    logo: "logo.svg"
    front_img: "front_img.jpg"
    img_to_dark: TRUE
    logo_to_white: TRUE
  officedown::rdocx_document:
    reference_docx: docx_template.docx
    toc: yes
  officedown::rpptx_document:
    reference_doc: pptx_template.pptx
    slide_level: 2
mainfont: Avenir
geometry: left=2cm,right=2cm,top=2.5cm,bottom=2cm
params:
  rendered_by_shiny: false
  todays_date: NA
  contacts_df_long: NA
  report_format: NA
#knit: pagedown::chrome_print
google-font: TRUE
main-font: "Open Sans"
fontsize: 10pt
main-color: "#3391CF"
---

<!-- tag_to_pull_do_not_remove -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, dpi = 300, eval = TRUE)

# ~~~~ Progress tracker  ----
number_of_chunks <- 34
current_chunk <- 0

update_rmd_progress <- function(){
  if (params$rendered_by_shiny) {
  current_chunk <<- current_chunk + 1
  shiny::setProgress(current_chunk/number_of_chunks, 
                     detail = paste0("Building section ", 
                                      current_chunk, 
                                      " of ", 
                                      number_of_chunks ))
  }
  
  if(current_chunk == number_of_chunks){
    
     shiny::setProgress(1, 
                        detail = "Finalizing report"
                        )
    
  }
  
}


## turn off highcharter animations
library(highcharter)

myMenuItems <-
  c(
    "printChart",
    "separator",
    "downloadPNG",
    "downloadJPEG",
    "downloadPDF",
    "downloadSVG",
    "separator",
    "viewData",
    "downloadCSV",
    "downloadXLS"
  )

newtheme <-
  hc_theme_merge(
    getOption("highcharter.theme"),
    hc_theme(plotOptions = list(series = list(animation = FALSE)),
             exporting = list(buttons = list(contextButton = list(menuItems = myMenuItems))))

    )
  

options(highcharter.theme = newtheme)

# 
# ## functions for documentation
# building_docs <-  TRUE
# 
# 
# print_def <- function(function_name) {
#   if (building_docs == TRUE) {
#     
#     function_def <-
#       capture.output(function_name) %>%
#       styler::style_text() %>% 
#         paste(collapse = "\n")
#     
#     ## print
#     cat(paste("```r", function_def, "```", sep = "\n"))
#     
#   }
# }
# 
# options(width=9999)
# 

```

```{css, echo=FALSE}
h1 {
  text - align:center
}
body {
  background - color:#f0f2fa
}

.tab - content{
  margin - bottom:70px
}

## avoid wrapping (horizontal scrollbar instead)
pre, code {white-space:pre !important; overflow-x:auto}
```

```{r paramsSetNonShiny}
## if we are knitting outside of shiny, we cannot rely on reactives.
## Thus, we run the functions manually
## At the end, we will output the cleaned dataframe for visualization

if (params$rendered_by_shiny == FALSE){
  
  source(here::here("global.R"))
  
  ## artificial input since we're not in shiny context
  input <- list()
  
  source(here::here("helper_scripts/server_functions.R")) 

  input$data_to_use <- "Use preloaded data"
  preloaded_data_options <-  preloaded_data_options ## defined in global file
  input$preloaded_data_choice <- "Sample tracing data"
  cols_to_exclude_from_filters <- c("placeholder_non_column")
  input$select_date_of_review <- as.Date("2021-04-13")
  
      
  report_format <- "html (page)"
  todays_date <- input$select_date_of_review

  url <- "https://godata-r13.who.int/"
  username <- "godata_api@who.int"
  password <- "godata_api@who"
  outbreak_id <- "3b5554d7-2c19-41d0-b9af-475ad25a382b"

  # ~~~~ read_file_raw ----
  
   tracing_data_raw <-
    read_file_raw()
  
  # ~~~~ read_file_transformed ----
  
  contacts_df_long_transformed <- 
    read_file_transformed(tracing_data_raw = tracing_data_raw)
  
  
# ~~~~ read_file_filtered ----
  
  contacts_df_long <- 
    read_file_filtered(contacts_df_long_transformed,
                       input$select_date_of_review)

  PARAMS$documentation <-  TRUE

}
  
```

```{r paramsSetShiny}
## if knitting within shiny
if (params$rendered_by_shiny == TRUE){
  
# ~~~~ Source functions  ----

  source(here::here("global.R"))
  source(here::here("helper_scripts/server_functions.R")) 


  ## parameters
  contacts_df_long <- params$contacts_df_long
  todays_date <- params$todays_date
  report_format <- params$report_format
}


update_rmd_progress()
```

# VALUE BOX SUMMARIES

```{r valueBoxes1, fig.width=3.5, fig.height=2, out.width="48%"}
new_contacts_per_day_value_box(contacts_df_long,
                           todays_date,
                           report_format)

cumulative_contacts_value_box(contacts_df_long,
                              todays_date,
                              report_format)

update_rmd_progress()
```

```{r valueBoxes2, fig.width=3.5, fig.height=2, out.width="48%"}

contacts_under_surveillance_value_box(contacts_df_long,
                                      todays_date,
                                      report_format)

pct_contacts_followed_value_box(contacts_df_long,
                                todays_date,
                                report_format)


update_rmd_progress()
```

<!------------------>
<!-- NEW CONTACTS -->
<!------------------>

```{r results = "asis"}
new_contacts_today_row_title(todays_date, report_format)
```

##  {.unlisted .unnumbered}

```{r results = "asis"}
new_contacts_today_text(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```

### New contacts bar chart

```{r}
new_contacts_today_bar_chart(contacts_df_long,
                        todays_date,
                        report_format)
update_rmd_progress()
```

### New contacts sunburst plot

```{r}
new_contacts_today_sunburst_plot(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```

### New contacts table

```{r}
new_contacts_today_table(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```


<!-- new contacts historical -->


```{r results = "asis"}
new_contacts_historical_row_title(report_format)
```

##  {.unlisted .unnumbered}

```{r, results = "asis"}
new_contacts_historical_text(contacts_df_long,
                                 todays_date,
                                 report_format)
update_rmd_progress()
```

### Absolute numbers

```{r}
new_contacts_historical_bar_chart(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

### Relative proportions

```{r}
new_contacts_historical_bar_chart_relative(contacts_df_long,
                                               todays_date,
                                               report_format)
update_rmd_progress()
```

<!------------------------>
<!-- CUMULATIVE CONTACTS -->
<!------------------------>


```{r results = "asis"}
cumul_contacts_today_row_title(todays_date, report_format)
```

##  {.unlisted .unnumbered}

```{r results = "asis"}
cumul_contacts_today_text(contacts_df_long,
                        report_format)

update_rmd_progress()
```

### Cumulative contacts bar chart

```{r}
cumul_contacts_today_bar_chart(contacts_df_long,
                        report_format)
update_rmd_progress()
```

### Cumulative contacts sunburst plot

```{r}
cumul_contacts_today_sunburst_plot(contacts_df_long,
                        report_format)

update_rmd_progress()
```

### Cumulative contacts table

```{r}
cumul_contacts_today_table(contacts_df_long,
                        report_format)

update_rmd_progress()
```


<!-- cumul contacts historical -->


```{r results = "asis"}
cumul_contacts_historical_row_title(report_format)
```

##  {.unlisted .unnumbered}

```{r, results = "asis"}
cumul_contacts_historical_text(contacts_df_long,
                                 report_format)
update_rmd_progress()
```

### Absolute numbers

```{r}
cumul_contacts_historical_bar_chart(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

### Relative proportions

```{r}
cumul_contacts_historical_bar_chart_relative(contacts_df_long,
                                               todays_date,
                                               report_format)
update_rmd_progress()
```


<!------------------>
<!-- ACTIVE CONTACTS -->
<!------------------>

```{r results = "asis"}
active_contacts_today_row_title(todays_date, report_format)
```

##  {.unlisted .unnumbered}

```{r results = "asis"}
active_contacts_today_text(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```

### Contacts under surveillance bar chart

```{r}
active_contacts_today_bar_chart(contacts_df_long,
                        todays_date,
                        report_format)
update_rmd_progress()
```

### Contacts under surveillance sunburst plot

```{r}
active_contacts_today_sunburst_plot(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```

### Contacts under surveillance table

```{r}
active_contacts_today_table(contacts_df_long,
                        todays_date,
                        report_format)

update_rmd_progress()
```


<!-- active contacts historical -->


```{r results = "asis"}
active_contacts_historical_row_title(report_format)
```

##  {.unlisted .unnumbered}

```{r, results = "asis"}
active_contacts_historical_text(contacts_df_long,
                                 todays_date,
                                 report_format)
update_rmd_progress()
```

### Absolute numbers

```{r}
active_contacts_historical_bar_chart(contacts_df_long,
                                      todays_date,
                                      report_format)
update_rmd_progress()
```

### Relative proportions

```{r}
new_contacts_historical_bar_chart_relative(contacts_df_long,
                                               todays_date,
                                               report_format)
update_rmd_progress()
```


# Contacts per case

##  {.unlisted .unnumbered}

```{r totalContactsPerCaseText, results = "asis"}
total_contacts_per_case_text(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Contacts per case, table

```{r totalContactsPerCaseTable}
total_contacts_per_case_table(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Contacts per case, donut plot

```{r totalContactsPerCaseDonutPlot}
total_contacts_per_case_donut_plot(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Contacts per case, bar chart

```{r totalContactsPerCaseBarChart}
total_contacts_per_case_bar_chart(contacts_df_long,
                             report_format)

update_rmd_progress()
```

# Case-contact relationships

##  {.unlisted .unnumbered}

```{r totalContactsPerLinkTypeText, results = "asis"}
total_contacts_per_link_type_text(contacts_df_long,
                                        report_format)

update_rmd_progress()
```

### Case-contact relationships, donut plot

```{r totalContactsPerLinkTypeDonutPlot}
total_contacts_per_link_type_donut_plot(contacts_df_long,
                             report_format)

update_rmd_progress()
```

### Case-contact relationships, bar chart

```{r totalContactsPerLinkTypeBarChart}
total_contacts_per_link_type_bar_chart(contacts_df_long,
                             report_format)

update_rmd_progress()
```

# Follow-up timelines

##  {.unlisted .unnumbered}

```{r activeContactsTimelineText, results = "asis"}
active_contacts_timeline_text(contacts_df_long,
                             todays_date,
                             report_format)
```

### Follow-up summary bar chart

```{r activeContactsBreakdownBarChart, fig.width = 7, dpi = if(params$report_format %in% c("html (page)", "html (slides)")) {96} else {300} }
active_contacts_breakdown_bar_chart(contacts_df_long,
                           todays_date,
                           report_format,
                           legend_df)

update_rmd_progress()

```

### Follow-up timeline snake plot

```{r activeContactsTimelineSnakePlot, fig.width = 7, dpi =  if(params$report_format %in% c("html (page)", "html (slides)")) {96} else {300} }
active_contacts_timeline_snake_plot(contacts_df_long,
                           todays_date,
                           report_format,
                           legend_df)

update_rmd_progress()
```

# Contacts not seen recently

##  {.unlisted .unnumbered}

```{r lostContactsLinelistText, results = "asis"}
lost_contacts_linelist_text(contacts_df_long,
                             todays_date,
                             report_format)
update_rmd_progress()
```

### Loss to follow-up, past 3 days

```{r contactsLost24To72HoursTable}
contacts_lost_24_to_72_hours_table(contacts_df_long,
                             todays_date,
                             report_format)
```

### List of contacts not seen

```{r lostContactsLinelistTable, results = "asis"}

lost_contacts_linelist_table(contacts_df_long,
                             todays_date,
                             report_format = report_format) %>%
  .$output_table

```
