---
title: "02: server.R"
output:
 rmarkdown::html_document:
   toc: yes
   toc_depth: 2
   toc_float: yes
params:
 building_docs: true
---

```{r include=FALSE}
## for knitting into documentation file

if(exists("params") && !is.null(params$building_docs) && params$building_docs == TRUE ){
  knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
}
```

NOTE: Section headers on this file are duplicated. 
One set of headers exist for knitting this to an Rmarkdown (for documentation)
The second set are hooks for RStudio's document outline feature.
Increase upload size. See https://shiny.rstudio.com/articles/upload.html

```{r }
options(shiny.maxRequestSize = 50 * 1024^2)
```

# Source server functions

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Source server functions ------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Load in the primary functions that will be called within server.R

```{r }
  source(here::here("helper_scripts/server_functions.R"), local = T)
```

# Country-specific load data UI

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Country-specific load data UI ------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Here we call the function that loads all the country-specific
UI elements required in the "Choose dataset to analyse" box. 

```{r }
  country_specific_UI_for_loading_data(input = input, output = output)
```

# Load data reactives

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Load data reactives --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Each of the "read_file-" reactives sources its namesake function.
These functions are called in a reactive context to ensure that if the input data changes, 
all the output graphs will change as well.
## read_file_raw_reactive

```{r }
# ~~~~ read_file_raw_reactive --------------------
```

The read_file_raw function does either of two things.
- For countries using Go.Data, it takes in the input credentials, 
logs into a Go.Data session, and returns a list with the requisite dataframes.
- For countries using KoboCollect, it takes in the two uploaded csv files, 
(contact list and follow-up list), and returns them as a list of a dataframes.

```{r }
  read_file_raw_reactive <- reactive({
    req(input$data_to_use)
    req(input$analyze_action_bttn)

    read_file_raw()
  })
```

## read_file_transformed_reactive

```{r }
# ~~~~ read_file_transformed_reactive -----------------
```

The 'read_file_transformed' function takes in data from read_file_raw_reactive, 
and 'transforms' it into a single, 'long' dataframe,
with one row per contact-follow-up-day

```{r }
  read_file_transformed_reactive <- reactive({
    req(input$data_to_use)
    req(input$analyze_action_bttn)

    read_file_transformed(tracing_data_raw = read_file_raw_reactive())
  })


  #' ## read_file_filtered_reactive
  # ~~~~ read_file_filtered_reactive ------------------------
  #' The 'read_file_filtered' function takes in data from read_file_transformed_reactive 
  #' It also takes in a date_of_review variable.
  #' It filters out contacts who had not begun followup by the selected date_of_review 
  #' Also, for contacts being followed, "future" are relabelled as such. 
  #' The output of read_file_filtered is a df that feed most graphs in the app. 

  read_file_filtered_reactive <- reactive({
    req(input$analyze_action_bttn)

    read_file_filtered(contacts_df_long_transformed = read_file_transformed_reactive(), 
                       todays_date = input$select_date_of_review)
  })
```

# Action button observer

```{r }
# ~~~~  Action button observer ---------------------------
```

This observer simply triggers or re-triggers 'read_file_transformed_reactive' 
whenever the analyze action button is pressed

```{r }
  observeEvent(input$analyze_action_bttn, {
    read_file_transformed_reactive()
  })
```

# Data overview section

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Data overview section----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

The plots below take in data from 'read_file_transformed_reactive' 
and output summary graphics.
Recall that the output of 'read_file_transformed_reactive' is 
the unfiltered, full, "long" dataframe, with one row per contact-follow-up-day.
## data_completeness_plot

```{r }
# ~~~~ data_completeness_plot ---------------------------
```

Here we output a visualization of the entire long dataframe.
Uses the viz_dat function

```{r }
  output$data_completeness_plot <-
    renderPlot({
      req(read_file_transformed_reactive())

      if (input$data_to_use == "Use uploaded data") {
        req(input$uploaded_data_contacts_list)
        req(input$uploaded_data_follow_up_list)
      }

      if (input$data_to_use == "Use preloaded data") {
        req(input$preloaded_data_choice)
      }


      read_file_transformed_reactive() %>%
        data_completeness_plot()
    })
```

## data_cardinality_plot

```{r }
# ~~~~  data_cardinality_plot ---------------------------
```

This is a plot using the 'inspect_cat' function of the inspectdf package 

```{r }
  output$data_cardinality_plot <-
    renderPlot({
      req(read_file_transformed_reactive())

      if (input$data_to_use == "Use uploaded data") {
        req(input$uploaded_data_contacts_list)
        req(input$uploaded_data_follow_up_list)
      }

      if (input$data_to_use == "Use preloaded data") {
        req(input$preloaded_data_choice)
      }

      read_file_transformed_reactive() %>%
        data_cardinality_plot()
    })
```

## reactable_table

```{r }
# ~~~~ reactable_table ---------------------------
```

Here, we output the entire long table for easy viewing, or searching

```{r }
  output$reactable_table <-
    renderReactable({
      req(read_file_transformed_reactive())

      if (input$data_to_use == "Use uploaded data") {
        req(input$uploaded_data_contacts_list)
        req(input$uploaded_data_follow_up_list)
      }

      if (input$data_to_use == "Use preloaded data") {
        req(input$preloaded_data_choice)
      }

      read_file_transformed_reactive() %>%
        reactable_table()
    })
```

# Date selection

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Date selection --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

This tab contains the primary graphs and tables that pertain to all contacts. 
(The next tab contains information pertaining to only active contacts, 
that is, contacts who are actively under surveillance)
## select_date_of_review

```{r }
# ~~~~ select_date_of_review --------------------
```

This picker lets you select a present or historical date, 
letting you see what the data looked like at each time point.
The range of dates that can be picked are bounded
by the range of dates in the dataframe (passed from 'read_file_transformed_reactive').
The picker also guesses what the date of review is. 
Basically, it obtains the last date for which follow-up status was not "missing" or "future",
(the last day on which there was any contact follow-up),
and assumes this is the date on which the user would like to view the data.

```{r }
  output$select_date_of_review <- renderUI({
    
    ## date selection needs to use the unfiltered data frame
    ## because the selection from this input feeds the filtering function
    req(input$data_to_use)
    req(read_file_transformed_reactive())
    
    
    flattened_dates <-
      read_file_transformed_reactive() %>%
      select(follow_up_date) %>%
      pull(1)
    
    min_date <- min(flattened_dates, na.rm = T)
    max_date <- max(flattened_dates, na.rm = T)
    
    # get the last date for which follow-up status was not "missing" or "future"
    # assume that that is the date as on which the data is being analyzed
    todays_date_imputed_from_data <-
      read_file_transformed_reactive() %>%
      filter(follow_up_status != "Suivi futur" &
               follow_up_status != "Manquant" &
               follow_up_status != "Future follow-up" &
               follow_up_status != "NA" &
               !is.na(follow_up_status)) %>%
      select(follow_up_date) %>%
      pull(1) %>%
      max(na.rm = T)
    
    dateInput("select_date_of_review",
              label = "Select date of review",
              value = todays_date_imputed_from_data,
              min = min_date,
              max = max_date
    )
  })
```

# Generate downloadable report

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Generate downloadable report --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

## select_report_format
Select which of five formats to use for the downloaded report.
(As at May 13, 2021, the PDF format is not working. 
Should hopefully work when this issue is sorted by the RStudio team: https://bit.ly/3oj0Kkv
)

```{r }
# ~~~~ select_report_format---------------------------
  output$select_report_format <- renderUI({
    
    req(input$select_date_of_review)
    
    selectInput("report_format",
                label = "Select format",
                choices = c(
                  "pptx",
                  "docx",
                  #"pdf",
                  "html (page)",
                  "html (slides)"
                )
    )
  })
```

## download_report_button
This is placed within a renderUI context so that we can hide it conditionally

```{r }
# ~~~~ download_report_button---------------------------
  output$download_report_button <- renderUI({
    
    req(input$select_date_of_review)
    
    tagList(
      HTML("<p style='font-size:4px'>  <br><br>  </p>"),
      downloadBttn("report",
                   label = "Download report",
                   style = "jelly",
                   color = "primary", size = "md"
      )
    )
  })
```

## download_report_function

```{r }
# ~~~~ download_report_function---------------------------

output$report <- download_report_function()
```

#  Dynamic filtering section

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Dynamic filtering section --------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

## filters
A dynamic filtering section. The code below renders an input picker for each 
column in the dataset. The code is quite hairy, but we have tried to comment it extensively.

```{r }
# ~~~~ ouput$filters----

  output$filters <- renderUI({
    req(input$analyze_action_bttn)
    req(input$select_date_of_review)
    req(input$filter_or_not)

    ## filters are only generated if the filter_or_not slider is set to TRUE
    if ((!is.null(input$filter_or_not)) && input$filter_or_not == TRUE) {
      
      my_data <-
        read_file_transformed_reactive() %>%
        as.data.frame() %>% ## not sure why but tibble doesn't work
        ## filters not created for rows that change across each contact
        select(-any_of(cols_to_exclude_from_filters)) %>%
        ## no filters for columns that are all NA
        janitor::remove_empty(which = "cols")
      
      
      labels <- sort(names(my_data))
      
      
      ## unique values of each column
      choices <- lapply(1:length(labels), function(x) {
        unique(my_data[, labels[x]])
      })
      

      ## render a selector for each column
      lapply(1:length(labels), function(i) {
        
        ## create output$gender, output$region and so on based on column names
        output[[labels[[i]]]] <- renderUI({
          
          ## first subset the data to that column
          col <- my_data[, labels[i]]
          
          ## then, below, we render an input picker based on whether the column is a character, number or date
          ## and also based on whether or not the column has NA values
          
          ## CHARACTER AND FACTOR COLUMNS  ~~~~~~~~~~~~~~~~~~~
          if (is.character(col) | is.factor(col)) {
            
            ## calc unique length to decide whether to add search bar
            length_choices <- length(na.omit(choices[[i]]))
            search_or_not <- if(length_choices >= 10 ) TRUE else FALSE
            
            ## create pickerInput. 
            ## this would be accessed as input$gender, input$region and so on
            input_UI_element <-  
              pickerInput(inputId = labels[[i]],
                          label = labels[[i]],
                          choices = na.omit(choices[[i]]),
                          selected = na.omit(choices[[i]]),
                          options = list(`actions-box` = TRUE, 
                                         `virtual-scroll`	= TRUE, 
                                         `live-search` = search_or_not,
                                         `live-search-placeholder` = "Enter search term",
                                         `dropup-auto` = FALSE),
                          multiple = TRUE)
            ## if col has NA values, add checkboxinput asking whether to keep these
            if (any(is.na(col))) {
              tagList(
                input_UI_element, 
                checkboxInput(inputId = paste0("na_", labels[[i]]),
                              label = paste0("Include contacts w. missing values for ",
                                             labels[[i]], "?"),
                              value = TRUE))
              ## otherwise, print/return just the primary input picker
              } else { input_UI_element }
            
            
            ## NUMERIC COLUMNS  ~~~~~~~~~~~~~~~~~~~
            ## same procedure as with character columns
          } else if (is.numeric(col)) {
            input_UI_element <- 
              sliderInput(inputId = labels[[i]],
                          label = labels[[i]],
                          min = min(col, na.rm = TRUE),
                          max = max(col, na.rm = TRUE),
                          value = c(min(col, na.rm = TRUE), 
                                    max(col, na.rm = TRUE)))
            ## if col has NA values, add checkboxinput asking whether to keep these
            if (any(is.na(col))) {
              tagList(
                input_UI_element, 
                checkboxInput(inputId = paste0("na_", labels[[i]]),
                              label = paste0("Include contacts w. missing values for ",
                                             labels[[i]], "?"),
                              value = TRUE))
              ## otherwise, print/return just the primary input picker
            } else { input_UI_element }
            
            
            ## DATE COLUMNS  ~~~~~~~~~~~~~~~~~~~
          } else if (lubridate::is.Date(col)) {
            input_UI_element <- 
              dateRangeInput(inputId = labels[[i]],
                             label = labels[[i]],
                             min = min(col, na.rm = TRUE),
                             max = max(col, na.rm = TRUE),
                             start = min(col, na.rm = TRUE),
                             end = max(col, na.rm = TRUE))
            ## if col has NA values, add checkboxinput asking whether to keep these
            if (any(is.na(col))) {
              tagList(
                input_UI_element, 
                checkboxInput(inputId = paste0("na_", labels[[i]]),
                              label = paste0("Include contacts w. missing values for ",
                                             labels[[i]], "?"),
                              value = TRUE))
              ## otherwise, print/return just the primary input picker
            } else { input_UI_element }
            
          }
          })
        
      }
      )
            

      ## the large lapply function above created an input picker for each column
      ## now we output all those input pickers, 
      ## as in uiOutput("gender") and so on.
      lapply(1:length(labels), function(i) {
        uiOutput(labels[[i]])
        })
    }
    
    ## these uiOutputs are packaged into a larger output, output$filters, 
    ## which will, finally, be placed in our UI, as in uiOutput("filters")
  })

  output$additional_filters_text <- renderUI({
    req(input$filter_or_not)

    if ((!is.null(input$filter_or_not)) && input$filter_or_not == TRUE) {
      tagList(
        h6("Use the input pickers and sliders to filter your data"),
        HTML("<font size='1'>
            Note that the following are not shown: <br>
          • Empty columns; <br>
          • Name columns; and <br>
          • the date of follow-up column <br>
          Also note that the options for each filter 
          do not react to selections on other filters.
                               </font>")
      )
    } else {
      HTML(c(" "))
    }
  })
```

#  OUTPUTS PERTAINING TO ALL CONTACTS

```{r }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ OUTPUTS PERTAINING TO ALL CONTACTS ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

#  Value boxes

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ Value boxes  --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Below we call the value-box functions and return their outputs.
These functions return an HTML Shiny value-box when the report_format parameter
is "shiny", and a ggplot-based value-box otherwise.
Like most of the remaining functions that the app uses, these take in 
two primary inputs: the long contacts dataframe (one row per follow-up-day), 
and the date of review.
## new_contacts_per_day_value_box

```{r }
# ~~~~ new_contacts_per_day_value_box ----
  
  output$new_contacts_per_day_value_box <-
    renderValueBox({
      
      req(input$select_date_of_review)
      req(input$analyze_action_bttn)
      
      ## require that there is actually data to be visualized
      shiny::validate(need(nrow(read_file_filtered_reactive()) > 0, message = FALSE))

      new_contacts_per_day_value_box(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review)
    })
```

## cumulative_contacts_value_box

```{r }
# ~~~~ cumulative_contacts_value_box ----
  
  output$cumulative_contacts_value_box <-
    renderValueBox({
      req(input$select_date_of_review)
      req(input$analyze_action_bttn)
      shiny::validate(need(nrow(read_file_filtered_reactive()) > 0, message = FALSE))

      cumulative_contacts_value_box(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review)
      
    })
```

## contacts_under_surveillance_value_box

```{r }
# ~~~~ contacts_under_surveillance_value_box ----  
  
  output$contacts_under_surveillance_value_box <-
    renderValueBox({
      req(input$select_date_of_review)
      req(input$analyze_action_bttn)
      shiny::validate(need(nrow(read_file_filtered_reactive()) > 0, message = FALSE))

      contacts_under_surveillance_value_box(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review)
      
    })
```

## pct_contacts_followed_value_box

```{r }
# ~~~~ pct_contacts_followed_value_box ----  
  
  output$pct_contacts_followed_value_box <-
    renderValueBox({
      req(input$select_date_of_review)
      req(input$analyze_action_bttn)
      shiny::validate(need(nrow(read_file_filtered_reactive()) > 0, message = FALSE))

      pct_contacts_followed_value_box(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review)
      
    })
```

# new_contacts_today

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ new_contacts_today  --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

These functions show the number of
of contacts over admin level 1 and admin level 2.
## new_contacts_today_row_title

```{r }
# ~~~~ new_contacts_today_row_title ----  

output$new_contacts_today_row_title <- renderUI({
  req(input$select_date_of_review)
  
  new_contacts_today_row_title(input$select_date_of_review)
  
})
```

## new_contacts_today_bar_chart

```{r }
# ~~~~ new_contacts_today_bar_chart ----  

output$new_contacts_today_bar_chart <-
  renderHighchart({
    req(input$select_date_of_review)
    
    new_contacts_today_bar_chart(
      contacts_df_long = read_file_filtered_reactive(), 
      todays_date = input$select_date_of_review
    )
  })
```

## new_contacts_today_sunburst_plot

```{r }
# ~~~~ new_contacts_today_sunburst_plot ----  

output$new_contacts_today_sunburst_plot <-
  renderHighchart({
    req(input$select_date_of_review)
    
    new_contacts_today_sunburst_plot(
      contacts_df_long = read_file_filtered_reactive(), 
      todays_date = input$select_date_of_review
    )
  })
```

## new_contacts_today_table

```{r }
# ~~~~ new_contacts_today_table ----  

output$new_contacts_today_table <-
  renderReactable({
    req(input$select_date_of_review)
    
    new_contacts_today_table(
      contacts_df_long = read_file_filtered_reactive(), 
      todays_date = input$select_date_of_review
    )
  })
```

## new_contacts_today_text

```{r }
# ~~~~ new_contacts_today_text ----  

output$new_contacts_today_text <-
  renderUI({
    req(input$select_date_of_review)
    
    new_contacts_today_text(
      contacts_df_long = read_file_filtered_reactive(), 
      todays_date = input$select_date_of_review
    )
  })
```

#  new_contacts_historical

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ new_contacts_historical  -----------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Functions showing how the number of contacts who are on follow-up day 1
## new_contacts_historical_row_title

```{r }
# ~~~~ new_contacts_historical_row_title ----  

output$new_contacts_historical_row_title <- renderUI({
  req(input$select_date_of_review)
  
  new_contacts_historical_row_title()
  
})
```

## new_contacts_historical_bar_chart

```{r }
# ~~~~ new_contacts_historical_bar_chart ----  

output$new_contacts_historical_bar_chart <-
  renderHighchart({
    req(input$select_date_of_review)
    
    new_contacts_historical_bar_chart(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

## new_contacts_historical_bar_chart_relative

```{r }
# ~~~~ new_contacts_historical_bar_chart_relative ----  

output$new_contacts_historical_bar_chart_relative <-
  renderHighchart({
    req(input$select_date_of_review)
    
    new_contacts_historical_bar_chart_relative(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

## new_contacts_historical_text

```{r }
# ~~~~ new_contacts_historical_text ----  

output$new_contacts_historical_text <-
  renderUI({
    req(input$select_date_of_review)
    
    new_contacts_historical_text(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

# cumul_contacts_today

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ cumul_contacts_today  --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Below we call the contacts_per_admin_1 functions. These show the distribution 
of contacts over admin level 1 and admin level 2.
## cumul_contacts_today_row_title

```{r }
# ~~~~ cumul_contacts_today_row_title ----  
  
  output$cumul_contacts_today_row_title <- renderUI({
    req(input$select_date_of_review)

    cumul_contacts_today_row_title(input$select_date_of_review)
    
  })
```

## cumul_contacts_today_table

```{r }
# ~~~~ cumul_contacts_today_table ----  
  
  output$cumul_contacts_today_table <-
    renderReactable({
      req(input$select_date_of_review)

      cumul_contacts_today_table(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## cumul_contacts_today_sunburst_plot

```{r }
# ~~~~ cumul_contacts_today_sunburst_plot ----  
  
  output$cumul_contacts_today_sunburst_plot <-
    renderHighchart({
      req(input$select_date_of_review)

      cumul_contacts_today_sunburst_plot(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## cumul_contacts_today_bar_chart

```{r }
# ~~~~ cumul_contacts_today_bar_chart ----  
  
  output$cumul_contacts_today_bar_chart <-
    renderHighchart({
      req(input$select_date_of_review)

      cumul_contacts_today_bar_chart(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## cumul_contacts_today_text

```{r }
# ~~~~ cumul_contacts_today_text ----  
  
  output$cumul_contacts_today_text <-
    renderUI({
      req(input$select_date_of_review)

      cumul_contacts_today_text(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

#  cumul_contacts_historical

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ cumul_contacts_historical  -----------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Functions showing the cumulative number of contacts over time.
## cumul_contacts_historical_row_title

```{r }
# ~~~~ cumul_contacts_historical_row_title ----  

output$cumul_contacts_historical_row_title <- renderUI({
  req(input$select_date_of_review)
  
  cumul_contacts_historical_row_title()
  
})
```

## cumul_contacts_historical_bar_chart

```{r }
# ~~~~ cumul_contacts_historical_bar_chart ----  

output$cumul_contacts_historical_bar_chart <-
  renderHighchart({
    req(input$select_date_of_review)
    
    cumul_contacts_historical_bar_chart(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

## cumul_contacts_historical_bar_chart_relative

```{r }
# ~~~~ cumul_contacts_historical_bar_chart_relative ----  

output$cumul_contacts_historical_bar_chart_relative <-
  renderHighchart({
    req(input$select_date_of_review)
    
    cumul_contacts_historical_bar_chart_relative(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

## cumul_contacts_historical_text

```{r }
# ~~~~ cumul_contacts_historical_text ----  

output$cumul_contacts_historical_text <-
  renderUI({
    req(input$select_date_of_review)
    ## use the same function. 
    cumul_contacts_historical_text(
      contacts_df_long = read_file_filtered_reactive()
    )
  })
```

# active_contacts_today

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ active_contacts_today  --------------------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Below we call the contacts_per_admin_1 functions. These show the distribution 
of contacts over admin level 1 and admin level 2.
## active_contacts_today_row_title

```{r }
# ~~~~ active_contacts_today_row_title ----  

output$active_contacts_today_row_title <- renderUI({
 req(input$select_date_of_review)
 
 active_contacts_today_row_title(input$select_date_of_review)
 
})
```

## active_contacts_today_table

```{r }
# ~~~~ active_contacts_today_table ----  

output$active_contacts_today_table <-
 renderReactable({
   req(input$select_date_of_review)
   
   active_contacts_today_table(
     contacts_df_long = read_file_filtered_reactive(),
     todays_date = input$select_date_of_review
   )
 })
```

## active_contacts_today_sunburst_plot

```{r }
# ~~~~ active_contacts_today_sunburst_plot ----  

output$active_contacts_today_sunburst_plot <-
 renderHighchart({
   req(input$select_date_of_review)
   
   active_contacts_today_sunburst_plot(
     contacts_df_long = read_file_filtered_reactive(),
     todays_date = input$select_date_of_review
   )
 })
```

## active_contacts_today_bar_chart

```{r }
# ~~~~ active_contacts_today_bar_chart ----  

output$active_contacts_today_bar_chart <-
 renderHighchart({
   req(input$select_date_of_review)
   
   active_contacts_today_bar_chart(
     contacts_df_long = read_file_filtered_reactive(),
     todays_date = input$select_date_of_review
   )
 })
```

## active_contacts_today_text

```{r }
# ~~~~ active_contacts_today_text ----  

output$active_contacts_today_text <-
 renderUI({
   req(input$select_date_of_review)
   
   active_contacts_today_text(
     contacts_df_long = read_file_filtered_reactive(),
     todays_date = input$select_date_of_review
   )
 })
```

#  active_contacts_historical

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ active_contacts_historical  -----------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Functions showing how many contacts were under surveillance at each time point, 
segregated by region.
## active_contacts_historical_row_title

```{r }
# ~~~~ active_contacts_historical_row_title ----  

output$active_contacts_historical_row_title <- renderUI({
  req(input$select_date_of_review)
  
  active_contacts_historical_row_title()
  
})
```

## active_contacts_historical_bar_chart

```{r }
# ~~~~ active_contacts_historical_bar_chart ----  
  
  output$active_contacts_historical_bar_chart <-
    renderHighchart({
      req(input$select_date_of_review)

      active_contacts_historical_bar_chart(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

## active_contacts_historical_bar_chart_relative

```{r }
# ~~~~ active_contacts_historical_bar_chart_relative ----  
  
  output$active_contacts_historical_bar_chart_relative <-
    renderHighchart({
      req(input$select_date_of_review)

      active_contacts_historical_bar_chart_relative(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

## active_contacts_historical_text

```{r }
# ~~~~ active_contacts_historical_text ----  
  
  output$active_contacts_historical_text <-
    renderUI({
      req(input$select_date_of_review)

      active_contacts_historical_text(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

#  contacts_per_case

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ contacts_per_case  -----------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Functions that output the number of contacts linked to each case
At the moment (May 13, 2021), the Go.Data app version has no information for this column.
## total_contacts_per_case_donut_plot

```{r }
# ~~~~ total_contacts_per_case_donut_plot ----  
  
  output$total_contacts_per_case_donut_plot <-
    renderHighchart({
      req(input$select_date_of_review)
      
      total_contacts_per_case_donut_plot(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## total_contacts_per_case_table

```{r }
# ~~~~ total_contacts_per_case_table ----  
  
  output$total_contacts_per_case_table <-
    renderUI({
      req(input$select_date_of_review)
      
      total_contacts_per_case_table(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## total_contacts_per_case_bar_chart

```{r }
# ~~~~ total_contacts_per_case_bar_chart ----  
  
  output$total_contacts_per_case_bar_chart <-
    renderHighchart({
      req(input$select_date_of_review)

      total_contacts_per_case_bar_chart(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## total_contacts_per_case_text

```{r }
# ~~~~ total_contacts_per_case_text ----  
  
  output$total_contacts_per_case_text <-
    renderUI({
      req(input$select_date_of_review)

      total_contacts_per_case_text(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

#  contacts_per_link_type

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ contacts_per_link_type -----------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Functions that output the number of contacts for each type of link (e.g. family)
At the moment (May 13, 2021), the Go.Data app version has no information for this column.
## total_contacts_per_link_type_donut_plot

```{r }
# ~~~~ total_contacts_per_link_type_donut_plot ----  
  
  output$total_contacts_per_link_type_donut_plot <-
    renderHighchart({
      req(input$select_date_of_review)

      total_contacts_per_link_type_donut_plot(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## total_contacts_per_link_type_bar_chart

```{r }
# ~~~~ total_contacts_per_link_type_bar_chart ----  
  
  output$total_contacts_per_link_type_bar_chart <-
    renderHighchart({
      req(input$select_date_of_review)

      total_contacts_per_link_type_bar_chart(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

## total_contacts_per_link_type_text

```{r }
# ~~~~ total_contacts_per_link_type_text ----  
  
  output$total_contacts_per_link_type_text <-
    renderUI({
      req(input$select_date_of_review)

      total_contacts_per_link_type_text(
        contacts_df_long = read_file_filtered_reactive()
      )
    })
```

#  OUTPUTS PERTAINING TO ACTIVE CONTACTS

```{r }
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ OUTPUTS PERTAINING TO ACTIVE CONTACTS ----
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

#  active_contacts_bar_and_snake

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ active_contacts_bar_and_snake ------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Graphs showing active contacts by status
## active_contacts_breakdown_bar_chart

```{r }
# ~~~~ active_contacts_breakdown_bar_chart ----  
  
  output$active_contacts_breakdown_bar_chart <-
    renderPlotly({
      req(input$select_date_of_review)
      
      active_contacts_breakdown_bar_chart(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review,
        legend_df = legend_df
      )
    })
```

## active_contacts_breakdown_table

```{r }
# ~~~~ active_contacts_breakdown_table ----  
  
  output$active_contacts_breakdown_table <-
    renderReactable({
      req(input$select_date_of_review)
      
      active_contacts_breakdown_table(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

## active_contacts_breakdown_table_download

```{r }
# ~~~~ active_contacts_breakdown_table_download ---- 
  
  output$active_contacts_breakdown_table_download <-
    active_contacts_breakdown_table_download()
```

The snake plot shows the status of each active contact.
The user can drag to select contacts, and download the list of selected contacts.
## active_contacts_timeline_snake_plot

```{r }
# ~~~~ active_contacts_timeline_snake_plot ----  
  
  output$active_contacts_timeline_snake_plot <-
    renderPlotly({
      req(input$select_date_of_review)

      active_contacts_timeline_snake_plot(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review,
        legend_df = legend_df
      )
    })
```

## active_contacts_snake_plot_selected_table

```{r }
# ~~~~ active_contacts_snake_plot_selected_table ----  
  
  ## table with the contacts that were selected
  output$active_contacts_snake_plot_selected_table <-
    renderReactable({
      req(input$select_date_of_review)

      active_contacts_snake_plot_selected_table(
        contacts_df_long = read_file_filtered_reactive(),
        event_data("plotly_selecting")$customdata
      )
    })
```

## active_contacts_snake_plot_selected_table_download

```{r }
# ~~~~ active_contacts_snake_plot_selected_table_download ----  
  
  ## download handler for the selected table
  output$active_contacts_snake_plot_selected_table_download <-
    active_contacts_snake_plot_selected_table_download()
```

## active_contacts_timeline_table

```{r }
# ~~~~ active_contacts_timeline_table ----  
  
  ## This is the tabular version of the data shown with the bar chart
  output$active_contacts_timeline_table <-
    renderReactable({
      req(input$select_date_of_review)

      active_contacts_timeline_table(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

## active_contacts_timeline_table_download

```{r }
# ~~~~ active_contacts_timeline_table_download ----  
  
  output$active_contacts_timeline_table_download <-
    active_contacts_timeline_table_download()
```

## active_contacts_timeline_text

```{r }
# ~~~~ active_contacts_timeline_text ----  
  
  ## text highlighting the number of active contacts
  output$active_contacts_timeline_text <- renderUI({
    req(input$select_date_of_review)

    active_contacts_timeline_text(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

#  lost_contacts

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~ lost_contacts ------
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Tables (and their download handlers) summarizing the number of individuals lost to follow-up
## contacts_lost_24_to_72_hours_table

```{r }
# ~~~~ contacts_lost_24_to_72_hours_table ----  
  
  output$contacts_lost_24_to_72_hours_table <-
    render_gt({
      req(input$select_date_of_review)

      contacts_lost_24_to_72_hours_table(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      )
    })
```

## contacts_lost_24_to_72_hours_table_download

```{r }
# ~~~~ contacts_lost_24_to_72_hours_table_download ----  
  
  output$contacts_lost_24_to_72_hours_table_download <-
    contacts_lost_24_to_72_hours_table_download()
```

## lost_contacts_linelist_table

```{r }
# ~~~~ lost_contacts_linelist_table ----  
  
  output$lost_contacts_linelist_table <-
    renderReactable({
      req(input$select_date_of_review)

      lost_contacts_linelist_table(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      ) %>%
        .$output_table
    })
```

## lost_contacts_linelist_table_download

```{r }
# ~~~~ lost_contacts_linelist_table_download ----  
  
  output$lost_contacts_linelist_table_download <-
    lost_contacts_linelist_table_download()
```

## lost_contacts_linelist_table_title

```{r }
# ~~~~ lost_contacts_linelist_table_title ----  
```

The title needs to be dynamic because at database inception, there may only be 
one or two days of follow-up in total. In such cases, we cannot call the table
"number lost to follow-up over the past three days

```{r }
  output$lost_contacts_linelist_table_title <-
    renderUI({
      req(input$select_date_of_review)

      lost_contacts_linelist_table(
        contacts_df_long = read_file_filtered_reactive(),
        todays_date = input$select_date_of_review
      ) %>%
        .$table_title
    })
```

## lost_contacts_linelist_text

```{r }
# ~~~~ lost_contacts_linelist_text ----  
  
  output$lost_contacts_linelist_text <- renderUI({
    req(input$select_date_of_review)

    lost_contacts_linelist_text(
      contacts_df_long = read_file_filtered_reactive(),
      todays_date = input$select_date_of_review
    )
  })
```

