---
title: "01: global.R"
output:
 rmarkdown::html_document:
   toc: yes
   toc_depth: 2
   toc_float: yes
---
The global.R file is run once before your app starts. 
Any R objects created here global.R file become available to the app.R file, 
the ui.R and the server.R files. 
# Main parameters

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Main parameters ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

The application has been built to work with two main data sources: 
contact tracing data from KoboCollect-exported csv files,
and contact tracing data from a Go.Data instance (by direct API connection)
Here, at the beginning of the global.R file, 
we set the PARAMS$country_code variable to the country being worked on. 
This ensures that the correct data import elements are loaded in the app, 
either the elements for KoboCollect csv import and processing, 
or the elements for connecting to, and downloading from the Go.Data instance.

```{r }
PARAMS <- list()
#PARAMS$country_code <- "UGA"
#PARAMS$country_code <- "CDO"
PARAMS$country_code <- "CIV" 
PARAMS$testing_mode <- FALSE
PARAMS$fake_data <- TRUE
```

# Packages 

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Packages ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

I would normally load packages with `pacman::p_load` 
but I had some trouble with this when deploying to shiny 

```{r message=FALSE, warning=FALSE, fig.width=7}
library(remotes)
if (!webshot::is_phantomjs_installed()) webshot::install_phantomjs()
library(webshot)  ##  for screenshots of htmlwidgets when outputting
library(here) 
library(paletteer) ## for palettes
# remotes::install_github("jbkunst/highcharter")
library(highcharter)  ## most charts 
library(plotly) ## for the snake plot. highcharter renders this plot too slowly
library(shiny)
library(shinyjs)
library(shinyWidgets)
library(shinydashboard)
library(shinydashboardPlus) ## extends shinydashboard
library(shinycssloaders) ## spinners for when app elements are loading
library(fresh) ## easy theme changes
library(reactable) ## HTML tables
library(htmlwidgets) ## for prependContent function
library(reactablefmtr) ## additional elements for reactable tables
library(magrittr) ## I sometimes use the %<>% operator from here
library(lubridate) ## date wrangling
library(inspectdf) ## the inspect_cat function is used on first page of app
library(visdat) ##  vizdat function used on first page to visualize dataframe
library(stringi) ## some additional string manipulations not provided by stringr 
library(anytime) ## for the `anydate` function which does intelligent date parsing
library(glue) ## alternative to `paste`
library(janitor) ## some cleaning utilities
library(scales) ## for date and time scales
library(gt) ## for easily customizable HTML table
library(gtools) ## for the `mixedsort` function
# remotes::install_github("reconhub/linelist")
library(linelist) ## for the clean_variable_spellings function 
# remotes::install_github("tidyverse/rvest")
library(rvest) ## for the HTMLtotext function
library(pander) ## for some tables?
library(rio) ## easy importing
library(huxtable) ## tables that output to docx and powerpoint
library(flextable) ## called by huxtable in some functions
library(rmarkdown) ## for knitting the report
# remotes::install_github("davidgohel/officedown")
library(officedown) ## for PPTX docs etc.
library(pagedreport) ## for PDF reports 
library(promises) ## not sure
library(clock) ## not sure
library(charlatan) ## for creating fake data
library(httr) ## for pulling from godata API
library(jsonlite) ## convert json files to data frames
# remotes::install_github("amirmasoudabdol/preferably")
library(preferably) ## theme for documentation site
library(tidyverse) ## tidyverse called last to avoid masking
```

# Misc options

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Misc options ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

A few miscellaneous settings

```{r }
options(scipen = 999) # turn off scientific notation
set.seed(1) # fix seed
options(tibble.print_max = 35, tibble.print_min = 35) # personal preference
```

# Misc functions

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~~ Misc functions ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Random functions used throughout the application

```{r }
source(here("helper_scripts/misc_functions.R"), local = T)
```

# Set colors and themes

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~~ Set colors and themes ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```

Save some hex codes as named colors for use in app

```{r }
space_cadet <- "#1C2541"
white <- "#FFFFFF"
alice_blue <- "#D9F0FE"
light_gray <- "#ebebeb"
cinnabar <- "#E64B35"
coral <- "#ff7a4a"
peach <- "#FCDC9C"
bright_yellow_crayola <- "#FFB238"
spinner_color <- burnt_sienna <- "#EE6C4D"
```

Here we set the params for the `fresh` theme. 
The `fresh` package permits easy customization of shinydashboard colors.

```{r }
my_fresh_theme <-
  fresh::create_theme(
    fresh::adminlte_color(
      light_blue = white
    ),
    fresh::adminlte_sidebar(
      dark_bg = space_cadet,
      dark_hover_bg = cinnabar,
      dark_color = alice_blue
    ),
    fresh::adminlte_global(
      content_bg = white,
      box_bg = white,
      info_box_bg = light_gray
    )
  )
```

Set a color legend for each country/ app version.
This feeds the colors on active contacts plots (app tab 2)

```{r }
if (PARAMS$country_code == "CIV"){
  
legend_df <-
  tribble(
    ~breaks, ~colors,
    "Manquant", col2hex("black"),
    "Poursuite du suivi", col2hex("lightseagreen"),
    "Symptomatique, resultats attendus", col2hex("lightpink2"),
    "Devenu cas confirme", col2hex("orangered"),
    "Sorti sain", col2hex("darkolivegreen4"),
    "Deplacé", col2hex("wheat3"),
    "Not generated", col2hex("wheat4"),
    "Fin du suivi", col2hex("dodgerblue3"),
    "Suivi futur", col2hex("goldenrod"),
    "Future follow-up", col2hex("goldenrod"),
    "Decede", col2hex("purple3")
  ) %>%
  arrange(breaks) %>%
  mutate(breaks = fct_inorder(breaks)) %>%
  mutate(legend_index = row_number())

} else if (PARAMS$country_code == "UGA"){
legend_df <-
  tribble(
    ~breaks, ~colors,
    "Missed", col2hex("gray50"),
    "Missing", col2hex("black"),
    "Seen, Ok", col2hex("lightseagreen"),
    "Seen, Not Ok", col2hex("orangered"),
    "Not attempted", col2hex("wheat3"),
    "Not performed", col2hex("blueviolet"),
    "Not generated", col2hex("purple3"),
    "End of follow-up", col2hex("dodgerblue3"),
    "Future follow-up", col2hex("goldenrod")
  ) %>%
  arrange(breaks) %>%
  mutate(breaks = fct_inorder(breaks)) %>%
  mutate(legend_index = row_number())
}
```

# Highcharter themes

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~~ Highcharter themes ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# ~~~~ Palette ----
highcharter_palette_initial <- c(
  "#332859",
  (
    paletteer_d("ggsci::nrc_npg") %>%
      as.character() %>%
      str_sub(1, 7)
  )
)
## for graphs with many categories
ramped_colors <- colorRampPalette(highcharter_palette_initial)(15)

## remove first and last colors from ramp, because these are the initial colors
new_colors <-
  ramped_colors[-c(1, length(ramped_colors))] %>%
  rev()
## combine to final palette
highcharter_palette <- c(highcharter_palette_initial, new_colors)
```

## Menu items for highcharter

```{r }
# ~~~~ Menu items for highcharter ----

myMenuItems <-
  c(
    "printChart",
    "separator",
    "downloadPNG",
    "downloadJPEG",
    "downloadPDF",
    "downloadSVG",
    "separator",
    "viewData",
    "downloadCSV",
    "downloadXLS"
  )
```

## Combine into final theme

```{r }
# ~~~~ Combine into final theme ----
newtheme <-
  hc_theme_merge(
    getOption("highcharter.theme"),
    hc_theme(
      chart = list(
        backgroundColor = "transparent",
        zoomType = "xy",
        panning = list(enabled = TRUE, type = "xy"),
        panKey = "shift"
      ),
      colors = highcharter_palette,
      labels = list(style = list(lineHeight = "100px")),
      plotOptions = list(series = list(label = list(
        style = list(lineHeight = "100px")
      ))),
      exporting = list(buttons = list(contextButton = list(menuItems = myMenuItems)))
    )
  )

options(highcharter.theme = newtheme)
```

## Theme for sparklines in value boxes

```{r }
# ~~~ Theme for sparklines in value boxes ----
```

This theme is very minimalist. Equivalent to theme_void in ggplot. 
Still hoverable though.

```{r }
hc_theme_sparkline_vb <- function(...) {
  theme <- list(
    chart = list(
      backgroundColor = NULL,
      margins = c(0, 0, 0, 0),
      spacingTop = 0,
      spacingRight = 0,
      spacingBottom = 0,
      spacingLeft = 0,
      plotBorderWidth = 0,
      borderWidth = 0,
      style = list(overflow = "visible")
    ),
    xAxis = list(
      visible = FALSE,
      endOnTick = FALSE,
      startOnTick = FALSE
    ),
    yAxis = list(
      visible = FALSE,
      endOnTick = FALSE,
      startOnTick = FALSE
    ),
    tooltip = list(
      outside = FALSE,
      shadow = FALSE,
      borderColor = "transparent",
      botderWidth = 0,
      backgroundColor = "transparent",
      style = list(textOutline = "5px white")
    ),
    plotOptions = list(
      series = list(
        marker = list(enabled = FALSE),
        lineWidth = 2,
        shadow = FALSE,
        fillOpacity = 0.25,
        color = "#FFFFFFBF",
        fillColor = list(
          linearGradient = list(x1 = 0, y1 = 1, x2 = 0, y2 = 0),
          stops = list(
            list(0.00, "#FFFFFF00"),
            list(0.50, "#FFFFFF7F"),
            list(1.00, "#FFFFFFFF")
          )
        )
      )
    ),
    credits = list(
      enabled = FALSE,
      text = ""
    )
  )

  theme <- structure(theme, class = "hc_theme")

  if (length(list(...)) > 0) {
    theme <- hc_theme_merge(
      theme,
      hc_theme(...)
    )
  }

  theme
}
```

## Plotly theme

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Plotly theme ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

font <- list(
  family = "Avenir",
  size = 15,
  color = "white"
)

label <- list(
  bordercolor = "transparent",
  font = font
)
```

## ggplot2 theme

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~~ ggplot2 theme ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

my_theme <- theme_classic() +
  theme(
    plot.title = element_text(face = "bold"),
    # plot.background = element_rect(fill = "gray93"),
    panel.grid.major = element_line(color = "gray95", size = 0.2),
    strip.background = element_blank(),
    # element textbox is from ggtext
    strip.text = ggtext::element_textbox(
      size = 11, face = "bold",
      color = "white", fill = "steelblue3", halign = 0.5,
      r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3)
    )
  )

theme_set(my_theme)
```

## Reactable theme

```{r }
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ~  Reactable theme ----
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~



options(reactable.theme = reactableTheme(
  stripedColor = "#f0f1fc70",
  backgroundColor = "#FFFFFF00",
  highlightColor = "#DADEFB",
  cellPadding = "4px 4px"
))
```

